Fivebranes

### 2022-05-30 fivebranes/twisted.tex
merge

In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given.
Within the BV formalism, the theory is only $\Z/2$ graded.
In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory which we recall here.

The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.

@@

In this paper a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
\[
\ell_k \colon L^{\times k} \to \Pi^k L 
\]
are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}

@@

The $L_\infty$ structure is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.

@@

The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
\[
U \subset S \times X 
\]
the cochain complex
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]

@@

@@

An explicit characterization of the holomorphic twist of a single fivebrane theory was given in \cite{SWtensor}. 
We briefly recall this desription.

@@

The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
\[
\alpha \in \Omega^{2,1}(X), \quad \omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \alpha + \dbar \omega & = 0 \\
\dbar \alpha = \dbar \phi_i & = 0 .
\end{split}
\eeqn

@@

In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\ZZ/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\leq 1, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]
The full space of BV fields is simply $\Pi \cL_{single}$.

@@

The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
\[
U \subset Z
\]
the cochain complex
\[
\clie^\bu\left(\cL_{single}(U)\right) .
\]

@@

The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting some number of fivebranes \brian{references}. 
In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting some number of holomorphically twisted fivebranes. 
We briefly recall the relevant setup here.

@@

Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\RR \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
If we remove this locus we obtain the following manifold 
\[
\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
\]
where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.

@@

For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(t;\lambda w , z).
\]
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(t;\lambda w , z).
\]
\end{itemize}

@@

In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$.

We first split the coordinates on the formal five-disk as
\[
(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
\]
In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.

Assign the following weights to the super Lie algebra $E(5|10)$. 
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
\end{itemize} 
The weight grading is concentrated in degrees $\geq -1$. 
In particular, there is a decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
\eeqn
with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
In particular 
\beqn 
\label{eqn:e36iso}
E(3|6) \cong V_0 \subset E(5|10)
\eeqn
is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.

We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \prod_{n \geq -1} V_n
\eeqn
Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
In particular, we have the following.

\begin{lem} 
The embedding $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
\[
E(3|6) \hookrightarrow \Hat{E(5|10)} .
\]
\end{lem}
%\begin{proof}
%It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
%Recall that the even cocycle defining this extension is 
%\[
%(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
%\]
%This is clearly zero since the image 
%\end{proof}

Notice that as a consequence of this decomposition there is a corresponding decomposition of local operators of the eleven-dimensional theory on $\C^5 \times \R$. 
By corollary \ref{cor:sugraops} there is a decomposition of $\Z/2$-graded cochain complexes 
\begin{align*}
\Obs_{sugra} (0) & = \clie^\bu \left( \Hat{V}_{-1} \times \prod_{n \geq 0} V_n \right) \\
& = \Sym(\Pi \Hat{V}^*_{-1}) \otimes \bigotimes_{n \geq 0} \Sym\left(\Pi V^*_n\right) .
\end{align*}
The differential $Q$, which is defined using the Lie bracket on $\Hat{E(5|10)}$ is of the form
$Q = Q_0 + \Hat{Q}$ where $Q_0$ acts on linear generators via
\[
Q_0 \colon V^*_n \to \oplus_{m + \ell = n} V^*_m \otimes V^*_\ell
\]
and $\Hat{Q}$ acts on linear generators via
\[
\Hat{Q} \colon \CC \to \oplus_{m + \ell + n = -1} V^*_m \otimes V^*_\ell \otimes V^*_n .
\]

>>>>

In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given.
Within the BV formalism, the theory is only $\Z/2$ graded.
In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.
We recall this description here.

The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold. 
We opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
The additional data of a theory in the BV formalism is a graded skew-symmetric pairing on this sheaf.

@@

In this paper $\Z/2$ graded $L_\infty$ algebra means a $\Z/2$ graded vector space~$L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
\[
\ell_k \colon L^{\times k} \to \Pi^k L 
\]
are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}

@@

The $L_\infty$ structure is described as follows. 
First, $\d = [-]_1$, the differential, is simply given by 
\begin{align*}
\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
\end{align*}
and $\d \gamma = \d \nu = 0$. 
For $k \geq 2$ the general formula for the $k$-ary brackets is 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}
In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
There is a sub sheaf given by the sections $\mu$ and $\nu$ which is $L_\infty$-equivalent to the sheaf of holomorphic divergence-free vector fields on $X$.

@@

In the BV formalism, the sheaf of fields of the eleven-dimensional theory is $\Pi \cL_{sugra}$. 
As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
In other words, as a $\Z/2$ graded commutative dg algebra, the classical observables of the eleven-dimensional theory supported on an open set $U \subset X \times S$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]

@@

Six-dimensional $\cN=(2,0)$ supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
\begin{itemize}
\item 
The holomorphic, or minimal, twist. 
This twist leaves three real directions invariant. 
The holomorphic twist of any $\cN=(2,0)$ theory can be defined on any complex three-fold $Z$ equipped with a square-root of its canonical bundle. 
\item 
The non-minimal twist. 
This twist leaves five real directions invariant.
The non-minimal twist of any $\cN=(2,0)$ theory can be defined on a six-manifold of the form $M^4 \times \Sigma$ where $M^4$ is a smooth four-manifold and $\Sigma$ is a Riemann surface. 
\end{itemize}

By standard arguments, the theory on a stack of $N$ fivebranes in flat space is a theory with $\cN=(2,0)$ supersymmetry. 
In later sections we provide arguments using the technology of twisted holography developed by Costello, Gaiotto, Li, and Paquette \cite{??} to provide a conjectural description of the twist of the theory for general $N > 1$. 
An explicit characterization of the holomorphic and non-minimal twists of a single fivebrane theory has been given in \cite{SWtensor}. 
We briefly recall this description.

@@

@@

The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $Z$:
\[
\alpha \in \Omega^{2,1}(Z), \quad \omega \in \Omega^{3,0}(Z),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(Z , K^{1/2}_Z) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \alpha + \dbar \omega & = 0 \\
\dbar \alpha = \dbar \phi_i & = 0 .
\end{split}
\eeqn

@@

In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\leq 1, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]
The full space of BV fields is simply $\Pi \cL_{single}$.

@@

The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
the cochain complex
\[
\clie^\bu\left(\cL_{single}(U)\right) .
\]

@@

The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting a number of fivebranes \brian{references}. 
In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting a number of holomorphically twisted fivebranes. 
We briefly recall the relevant setup here.

@@

Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\R \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
If we remove this locus we obtain the following manifold 
\[
\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
\]
where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.

@@

For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
\]
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
\]
\end{itemize}

@@
